### 2022-10-21 manuscript.Rmd
Devide simulations up in separate scripts, change to csv

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
    - "01_run_simulation.R"
---

@@

knitr::read_chunk(here::here("R", "funs.R"))
knitr::read_chunk(here::here("01_run_simulation.R"))
knitr::opts_chunk$set(echo = FALSE)

@@

@@

results_load_model3 <-
  readRDS(here::here("results_load_model3.rds"))
results_cov_model3  <- readRDS(here::here("results_cov_model3.rds"))

plot_cov_model3 <- results_cov_model3 %>%
  ggplot(aes(samplesize, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    size = 1.3
  ) +
  xlab('Sample size') + ylab('Power (%)') + ggtitle('A \n') +
  scale_color_discrete('Inter-factor \ncorrelation') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

plot_load_model3 <- results_load_model3 %>%
  ggplot(aes(samplesize, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    size = 1.3
  ) +
  xlab('Sample size') + ylab('Power (%)') + ggtitle('B \n') +
  scale_color_discrete('loading       \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

@@

results_load_model1 <-
  readRDS(here::here("results_load_model1.rds"))
results_load_model2 <-
  readRDS(here::here("results_load_model2.rds"))
results_cov_model2  <- readRDS(here::here("results_cov_model2.rds"))
results_load_model3 <-
  readRDS(here::here("results_load_model3.rds"))
results_cov_model3  <- readRDS(here::here("results_cov_model3.rds"))

plot_load_model1 <- results_load_model1 %>%
  ggplot(aes(samplesize, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A1 \n') +
  scale_color_discrete('loading    \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

plot_load_model2 <- results_load_model2  %>%
  ggplot(aes(samplesize, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A2 \n') +
  scale_color_discrete('loading \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots
plot_cov_model2 <- results_cov_model2 %>%
  ggplot(aes(samplesize, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('B1 \n') +
  scale_color_discrete('inter-factor \ncovariance') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0.0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

>>>>

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
    - R/run_simulation.R
  files:
    - intermediate_results_separability.zip
    - intermediate_results_reliability.zip
    - intermediate_results_type1error_1.zip
    - intermediate_results_type1error_2.zip
    - intermediate_results_type1error_3.zip
---

@@

knitr::read_chunk(here::here("R", "funs.R"))
knitr::read_chunk(here::here("R", "setup_simulation.R"))
knitr::read_chunk(here::here("R", "run_simulation_separability.R"))
knitr::opts_chunk$set(echo = FALSE)

@@

```{r}
intermediate_results <- here("intermediate_results/")
if(fs::dir_exists(intermediate_results))
 fs::dir_delete(intermediate_results)
unzip("intermediate_results_separability.zip", junkpaths = TRUE)
unzip(here("intermediate_results_reliability.zip"), junkpaths = TRUE)
unzip(here("intermediate_results_type1error_1.zip"), junkpaths = TRUE)
unzip(here("intermediate_results_type1error_2.zip"), junkpaths = TRUE)
unzip(here("intermediate_results_type1error_3.zip"), junkpaths = TRUE)
```

@@

results_load_model3 <- 
  read.csv(here::here("results_load_model3.csv"))
results_cov_model3 <- 
  read.csv(here::here("results_cov_model3.csv"))

plot_cov_model3 <- results_cov_model3 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    size = 1.3
  ) +
  xlab('Sample size') + ylab('Power (%)') + ggtitle('A \n') +
  scale_color_discrete('Inter-factor \ncorrelation') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

plot_load_model3 <- results_load_model3 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    size = 1.3
  ) +
  xlab('Sample size') + ylab('Power (%)') + ggtitle('B \n') +
  scale_color_discrete('loading       \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

@@

results_load_model1 <-
  read.csv(here::here("results_load_model1.csv"))
results_load_model2 <-
  read.csv(here::here("results_load_model2.csv"))
results_cov_model2  <-
  read.csv(here::here("results_cov_model2.csv"))
results_load_model3 <-
  read.csv(here::here("results_load_model3.csv"))
results_cov_model3  <- 
  read.csv(here::here("results_cov_model3.csv"))

plot_load_model1 <- results_load_model1 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A1 \n') +
  scale_color_discrete('loading    \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

plot_load_model2 <- results_load_model2  %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A2 \n') +
  scale_color_discrete('loading \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots
plot_cov_model2 <- results_cov_model2 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('B1 \n') +
  scale_color_discrete('inter-factor \ncovariance') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0.0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots
